---
  title: "Is Programming Relevant to CS1 Students’ Interests?"
  author: "Kevin Buffardi and Subhed Chavan"
  affiliation: "Computer Science Department, California State University-Chico"
  output:
    html_document:
      toc: true
---
        
## Presentation

This is a brief summary of *Is Programming Relevant to CS1 Students’ Interests?*, presented at [Consortium for Computing Sciences in Colleges, Northwest 2021](http://www.ccsc.org/northwest/2021/) and published in the Journal of Computing Sciences in Colleges.

## Research Questions

1. What popular interests do students perceive as **relevant** to CS/coding? 
2. What popular interests do students perceive as **not relevant** to CS/coding?
3. Are there differences in how interested different genders and races are in common CS1 applications?
4. Are there interests that uniquely appeal to gender and racial minorities?

```{r, include=FALSE}
library(DT)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
relevance <- read.csv("relevance.csv")
colnames(relevance) <- c("Interest","Relevant","Not Relevant","% Relevant")
relevance$`Total` <- relevance$`Relevant` + relevance$`Not Relevant`
datatable(relevance, options = list(
  searching = FALSE,
  pageLength = 15,
  paging=FALSE
  )
)
```
        